\documentclass[]{article}
\usepackage[utf8]{inputenc}

\title{Review of Initial Paper}
\date{}

\begin{document}	
	
\maketitle

The paper with the title "Sorting algorithm analysis" is in the scope.

Summary: this paper has as a main focus three sorting algorithms: Insertion Sort, Quick Sort and Heap Sort. They are not presented in "Introduction" section. The second section describes some aspects regarding the experiment environment and then each algorithm is explained, with a short explanation and example about how the algorithms actually work and which is the worst-case scenario for Insertion Sort and Quick Sort. The third section mentions all the details regarding the experiments environment. The results are then presented in the following section and are represented on a chart, with a short conclusion for each experiment. The conclusion makes a few remarks about the experiment results.

The undergone tests were made on randomly generated elements, on a number of 0, 1.000, 2.500, 5.000, 10.000, 25.000, 50.000, 100.000, 150.000, 200.000, 250.000, 500.000 and 1.000.000 elements. The experiments seem to be original and non-trivial. They also seem intuitively correct. Results seem to be of moderate importance.

The author doesn't master the field. The paper is not according to the standard. Presentation, style and format are of poor quality, making the presentation a mediocre one. From a structure point of view, the following sections are missing: "Abstract", "Related Work", "Future Work". The tile page doesn't have enough details. Various notations are used without explaining as the $\mathcal{O}$("Big $\mathcal{O}$") notation and the "References" section is not properly done.

Decision: Weak Reject

\end{document}